Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2020-07-26 paper/manuscript.tex
last check sec 1,2,3

%%%%%%%%%%%%%%%%%%%%
%  Introduction    %
%%%%%%%%%%%%%%%%%%%%
\todo[inline]{}The current Overleaf document is \url{https://www.overleaf.com/5136551543vgjqbkzpmqkp}
\section{What are alchemical free energy methods?}
\label{sec:intro}
Alchemical free energy calculations compute free energy differences associated with transfer processes, such as the binding of a small molecule to a receptor, the transfer of a small molecule from an aqueous to apolar phase~\cite{zwanzig1954hightemperature}, or the effects of protein side chain mutations on binding affinities or thermostabilities. 
 These calculations use non-physical\footnote{Here, the non-physical nature of the transformation is referred to as "alchemical", a term coined by Tembre and McCammon in Ref.~\cite{tembre1984ligandreceptor}.} intermediate states in which the chemical identity of some portion of the system (such as a small molecule ligand or protein sidechain) is changed by modifying the potential governing the interactions with the environment for the atoms being modified, inserted, or deleted.

Fig.~\ref{fig:fig_what_is_alchemy} illustrates common free energy changes that may be difficult to compute with unbiased molecular dynamics methods, but are more readily tractable with alchemical methods.
In alchemical simulations, the introduction of intermediate \textit{alchemical states} that bridge the high-probability regions of configuration space between the two physical endstates of interest permits the free energy of large transformations to be robustly computed.
Alchemical calculations can be used in a variety of scenarios, such as: 
\begin{itemize}
\item computing the free energy of a conformational change for a molecule with a high barrier to interconversion (Fig.~\ref{fig:fig_what_is_alchemy} \textbf{A});
\item computing partition ($\log P$) or distribution ($\log D$) coefficients between environments (Fig.~\ref{fig:fig_what_is_alchemy} \textbf{B})~\cite{rustenburg2016measuring, bosisio2016blinded} 
\item or between compartments or membranes (Fig.~\ref{fig:fig_what_is_alchemy} \textbf{C})~\cite{corey2019insights}. 
\end{itemize}

@@

Subsequent work in the 2000s led to improved implementations of alchemical methods in popular biomolecular simulation packages~\cite{shirts2003extremely,shirts2005solvation,vanderspoel2005gromacs, mermelstein2018fast, wang2015accurate, hedges2019biosimspace}. 
 This foundational work, combined with the methodological, technological, and hardware improvements of the last 5--10 years, have led to an explosion of interest and direct commercial application of the technologies~\cite{wang2015accurate, fratev2019improved, schindler2020largescale, cournia2017relative, sherborne2016collaborating}.

@@

%%%%%%%%%%%%%%%%%%%%
% Prerequesites    %
%%%%%%%%%%%%%%%%%%%%
\section{Prerequisites and Scope}
\label{sec:pre}
What can be expected from this Best Practices guide is a good starting point for new practitioners and a reference for experienced practitioners. 
 For this propose we provide a convenient checklist (Section~\ref{sec:checklist}) to help ensure all calculations comply with currently-understood best practices for alchemical simulation and analysis. 
 Where the best practices are currently unsettled, we highlight areas where further research is needed to identify an unambiguous recommendation.
 It can also serve as a set of best practices to ensure simulation robustness and reproducibility which reviewers may wish to consider as they evaluate papers.

 What we assume from a novice practitioner is a moderate experience with molecular simulation packages and concepts. 
 Furthermore, basic familiarity with the principles of molecular mechanics, molecular dynamics simulations, statistical mechanics, and the biophysics of protein-ligand association are essential. If you feel unfamiliar with some of these concepts, good starting points can be found in these references~\cite{braun2019best, grossfield2018best, klimovich2015guidelines, shirts2012best}.

@@

As some of the theoretical background can seem daunting, we do, however, provide a guide to the essential theory behind alchemical free energy calculations in Section~\ref{sec:theory}.

In the remainder of this paper, we will cover topics that are key to the preparation~(\ref{sec:prerequisites}), choice and use of correct protocols~(\ref{sec:simulation_protocol_choice}), and finally the best practices that should be used in the analysis of alchemical calculations~(\ref{sec:data_analysis}). 
Particular focus will be given to aspects of the molecular simulations which are unique to alchemical calculations---these include the calculation of transfer free energies (hydration free energies, partition coefficients, etc.), and binding free energies (absolute and relative).

@@

For convenience we have also compiled a list of common acronyms, common symbols used, and some essential terminology.
\begin{tcolorbox}[title=Acronyms, colback=blue!10!white]
    {\bf CPU} -- Central Processing Unit\\
     {\bf BAR} -- Bennett Acceptance Ratio\\
     {\bf FEP} -- Free Energy Perturbation\\
     {\bf GPCR} -- G-Protein Coupled Receptor\\
     {\bf GPU} -- Graphics Processing Unit\\
     {\bf MBAR} -- Multistate Bennett Acceptance Ratio\\
     {\bf MCSS} -- Maximum Common Substructure\\
     {\bf MD} -- Molecular Dynamics\\
     {\bf RMSE} -- Root Mean Square Error\\
     {\bf MUE} -- Mean unsigned error\\
     {\bf SAR} -- Structure-Activity Relationships\\
     {\bf TI} -- Thermodynamic Integration
\end{tcolorbox}

\begin{tcolorbox}[title=List of Symbols, colback=green!10!white]
$L$ and $R$ -- generic names for ligand and receptor\\
$K_b^{\circ}$ -- binding  constant \\
$c^{\circ}$ -- standard state concentration \\
$U$ -- potential energy\\
$u$ -- reduced potential describing a thermodynamic state \\
$\Delta G$ -- Gibbs free energy (isothermal isobaric ensemble)\\
$\Delta A$ -- Helmholtz free energy (canonical ensemble)\\
$\Delta f$-- reduced (dimensionless) free energy \\
$\Delta \hat{f}$ -- estimate from an estimator for the reduced free energy\\
$\Gamma$ -- conformation space accessible by simulations \\
$\vec{q}$ -- vector of a single configuration, i.e. $x$, $y$, $z$ coordinates of the simulation system\\
$k_B$ -- Boltzmann constant \\
$Z$ -- partition function \\
$p$ -- pressure \\
$\mu$ -- chemical potential (grand canonical ensemble)\\
$T$ -- temperature \\
$\beta \equiv (k_B T)^{-1}$ -- inverse thermal energy \\
$\vec{\lambda}$ -- alchemical progress parameter \\
$g$ -- statistical inefficiency\\
$\omega$ - overlap matrix\\
$C_t$- discrete-time-normalized fluctuation auto-correlation function\\
$\tau _{eq}$ - integrated auto-correlation time\\
$t_0$ - equilibration time
\end{tcolorbox}

@@

\subsection{Simulating binding events of receptor-drug systems can be computationally expensive}
Suppose you want to compute the binding affinity, or free energy of binding, of a ligand $L$ to a receptor $R$, given by:
\begin{equation}
R+L \leftrightharpoons RL
\end{equation}
The binding constant ($K_b^{\circ}$) is given by the law of mass action as the ratio of concentrations of product $[RL]$ and reactants $[R]$, $[L]$:
\begin{equation}
 K_b^{\circ} = c^{\circ}\frac{[RL]}{[L][R]}.
\end{equation}
The standard state concentration $c^\circ$ depends on the reference state, but it is usually set to $1\,\mathrm{mol}/\mathrm{L}$ assuming a constant pressure of $1\,\mathrm{atm}$ (see also Section~\ref{sec:standardstate-restraints}).
Thus, the Gibbs free energy of binding $\Delta G_{\mathrm{bind}}$ is given by:
\begin{equation}
    \Delta G_{\mathrm{bind},L} = -k_BT\ln K_b^{\circ},
\end{equation}
where $k_B$ is the Boltzmann constant and $T$ the temperature of the system.

\paragraph{The free energy of binding can be expressed as a ratio of partition functions}
A natural though generally very computational expensive way to estimate the equilibrium constant is by directly simulating several binding and unbinding events and computing the probability of finding the receptor-ligand system in the bound state, $P(RL)$, or the unbound state, $P(R+L)$.
Assuming the volume change upon binding to be negligible, which is often the case at $1~\mathrm{atm}$ due to the incompressibility of water, then the Gibbs free energy $\Delta G_{\mathrm{bind}, L}$ is approximately equal to the Helmholtz free energy $\Delta A_{\mathrm{bind}, L}$, and we can simulate the system in a box of volume $V$ to obtain~\cite{jong2011determining}
\begin{equation}\label{eq:binding-free-energy-from-bound-unbound-probability-ratio}
    \Delta G_{\mathrm{bind},L} \approx \Delta A_{\mathrm{bind}, L} = - k_B T  \left( \mathrm{ln} \frac{P(RL)}{P(R+L)} + \ln \left( c^\circ N_{\mathrm{Av}} V \right) \right) \, ,
\end{equation}
where $N_{\mathrm{Av}}$ is the Avogadro number, and the last term corrects for the simulated concentration being different than the standard concentration.
Let $\Gamma_{\mathrm{bound}}$ and $\Gamma_{\mathrm{unbound}}$ be the set of receptor-ligand conformations $\vec{q}$ that we consider bound and unbound respectively.
The probability of a conformation $\vec{q}$ is given by the Boltzmann probability density function
\begin{equation}
    P(\vec{q}) = \frac{\exp\left( \beta U(\vec{q}) \right)}{\int_{\Gamma} \exp\left( \beta U(\vec{q}) \right) \, d\vec{q}} \, ,
    \label{eq:conf_probability}
\end{equation}
where $\beta = (k_B T)^{-1}$ is the inverse temperature, $U(\vec{q})$ is the potential energy of conformation $\vec{q}$, and the integration is over the set of all possible conformations accessible in the simulation box volume $\Gamma$, with $\Gamma_{\mathrm{bound}},\Gamma_{\mathrm{unbound}} \subset \Gamma$.
If the simulation is long enough, we expect the fraction of conformations $\vec{q}$ found in the bound state to converge to
\begin{equation}
    P(RL) = \int_{\Gamma_{\mathrm{bound}}} P(\vec{q}) \, d\vec{q} = \frac{\int_{\Gamma_{\mathrm{bound}}} \exp\left( \beta U(\vec{q}) \right) \, d\vec{q}}{\int_{\Gamma} \exp\left( \beta U(\vec{q}) \right) \, d\vec{q}} \, .
\end{equation}
After similar considerations for $P(R+L)$, we find that the ratio of visited bound and unbound conformations, in the limit of long simulations, should converge to
\begin{equation}\label{eq:bound-unbound-probability-ratio}
    \frac{P(RL)}{P(R+L)} = \frac{\int_{\Gamma_{\mathrm{bound}}} \exp\left( -\beta U(\vec{q}) \right) \, d\vec{q}}{\int_{\Gamma_{\mathrm{unbound}}} \exp\left( -\beta U(\vec{q}) \right) \, d\vec{q}} = \frac{Z(RL)}{Z(R+L)} \, ,
\end{equation}
where we have defined the \textit{configurational integral} or \textit{partition function} $Z(\mathrm{state}) \equiv \int_{\Gamma_{\mathrm{state}}} \exp\left(-\beta U(\vec{q})\right) \, d\vec{q}$.

\paragraph{Simulating binding events is computationally expensive}
While simulating binding events has been used to estimate binding affinities~\cite{jong2011determining,pan2017quantitative} or to get insights into the binding pathways and kinetics of receptor-ligand systems~\cite{teo2016adaptive,votapka2017seekr,doerr2014onthefly,plattner2015protein,dixon2018predicting}, the computational cost of these calculations is usually dominated by the rate of dissociation, which can be on the {\textmu}s scale even for millimolar binders~\cite{pan2017quantitative} and reaches the ms or s scale for a typical drug~\cite{basavapathruni2012conformational,hyre2006cooperative}.
Depending on system size and simulation settings, common molecular dynamics software packages can reach a few hundreds of ns/day using currently available high-end GPUs~\cite{eastman2017openmm,kutzner2019more}, making these type of calculations uninteresting at pharmaceutical drug discovery timescales.
Other methods compute the free energy of binding by building potential of mean force profiles along a reaction coordinate~\cite{woo2005calculationa,velez-vega2013overcoming,limongelli2013funnel,heinzelmann2017attachpullrelease}, but these methods require prior knowledge of a high-probability binding pathway, which is not easily available, especially in the prospective scenarios typical of the drug development process.

@@

In many cases, the quantity of interest is the change in binding affinity when a compound $A$ is mutated to compound $B$ (e.g., by modifying one the drug scaffold's substituents, see Fig.~\ref{fig:fig_what_is_alchemy} \textbf{F}), which, by using Eq.~\ref{eq:binding-free-energy-from-bound-unbound-probability-ratio} and \ref{eq:bound-unbound-probability-ratio} is given by
\begin{equation}\label{eq:delta-delta-G-physical}
\begin{split}
    \Delta \Delta G_{\mathrm{bind}, AB} &= \Delta G_{\mathrm{bind}, B} - \Delta G_{\mathrm{bind}, A} \\
    &\approx -k_BT \left( \ln \frac{Z(RB)}{Z(R+B)} - \ln \frac{Z(RA)}{Z(R+A)} \right) \, .
\end{split}
\end{equation}
Note that the terms involving the standard concentration cancel out when we assume that the volume is identical for $A$ and $B$.
Predictions of $\Delta \Delta G_{\mathrm{bind}, AB}$ with non-alchemical methods generally require long simulations of both ligands, possibly through different binding pathways.
Alchemical relative free energy calculations avoid the need to simulate binding and unbinding events by making use of the fact that the free energy is a state function and exploiting the thermodynamic cycle illustrated in Fig.~\ref{fig:fig_binding_thermodynamic_cycle}.
This is apparent after rewriting Eq.~\ref{eq:delta-delta-G-physical} as
\begin{equation}\label{eq:delta-delta-G-alchemical}
\begin{split}
    \Delta \Delta G_{\mathrm{bind}, AB} &\approx -k_BT \left( \ln \frac{Z(RB)}{Z(RA)} - \ln \frac{Z(R+B)}{Z(R+A)} \right) \\
    &= -k_BT \left( \ln \frac{Z(RB)}{Z(RA)} - \ln \frac{Z(B)}{Z(A)} \right) \\
    &= \Delta G_{\mathrm{bound}} - \Delta G_{\mathrm{unbound}} \, ,
\end{split}
\end{equation}
where $\Delta G_{\mathrm{bound/unbound}}$ is the free energy of mutating $A$ to $B$ in the bound/unbound state.
Eq.~\ref{eq:delta-delta-G-alchemical} and Fig.~\ref{fig:fig_binding_thermodynamic_cycle} tell us that the difference in free energy of binding between toluene ($A$) and benzyl alcohol ($B$) can be computed by running two independent calculations estimating the free energy cost of mutating $A$ into $B$ in the binding pocket ($\Delta G_{\mathrm{bound}}$) and in solvent ($\Delta G_{\mathrm{unbound}}$), saving us the need to simulate the physical binding process of the two compounds.
In particular, the second line of Eq.~\ref{eq:delta-delta-G-alchemical} is a consequence of $\Delta G_{\mathrm{unbound}}$ being independent of the presence of the receptor in the simulation box as the definition of the unbound state assumes receptor and ligand to be at a sufficient distance for them to have no energetic interactions.
Note that, when $A$ and $B$ have different number of atoms, Eq.~\ref{eq:delta-delta-G-alchemical} implies the presence of a factor having units of volume entering both logarithms, which require unitless arguments.
However, the value of this factor is inconsequential as it cancels out in practice.

@@

\todo[inline, color={green!20}]{ASJSM: @JDC, Can you check the issues below? }
Sometimes free energy calculations can provide answers that are not
readily available from experiments.  For example, type II kinase
inhibitors selectively bind to different kinases in the so-called
DFG-out conformations~\cite{schindler2000structural}.  The selectivity of such
inhibitors may be attributed either to their differential binding to
different kinases in the DFG-out conformations, or to different
stability of the DFG-out conformations of different kinases.  Let
$K_C$ be the equilibrium constant between DFG-in and DFG-out
conformations of one kinase, and $K_D^\ast$ be the dissociation
constant of a type II inhibitor against this kinase, the apparent
binding constant of this inhibitor against this kinase is then
\begin{equation}
  K_D = K_D^\ast \frac{1 + K_C}{K_C}
  \label{eqn:conformational-binding}
\end{equation}

@@

If you are unsure whether your project is feasible, as mentioned above one recommended option is to conduct a short exploratory study to assess tractability for a small
number of ligands. This can be sufficient to get an initial
idea of feasibility and accuracy of the calculations for the
proposed target.
%
\section{How should alchemical simulations be applied to drug discovery?}
\label{sec:drugdiscovery}
Many practitioners expect alchemical methods to provide valuable guidance for drug discovery, and to exhibit accuracy superior to most alternative approaches for suitable targets~\cite{kuhn2017prospective}. Successful application in industry may require considerable knowledge of the ``domain of applicabilit'' of free energy calculations -- where they work well and where they will not~\cite{sherborne2016collaborating}. Successful application also requires robust protocols for preparing, submitting and analysing alchemical calculations. In this regard, the issues mentioned in the previous section such as understanding the suitability and timescales to capture the structure activity relationships (SAR), and performing up-front tests of performance are all relevant to drug discovery applications. Without venturing too far into details of system setup, which is beyond the scope of this article, we highlight some critical factors affecting accuracy and successful application. 
%
\subsection{Capturing experimental conditions}
The calculations aim to capture the alchemical change from one ligand to another as accurately as possible. Therefore, it is necessary to consider details of the experimental setup, such as pH. Biological assays are usually run at neutral pH but this is not always the case, and protein and ligand preparation protocols should reflect experimental pH.

@@

In some cases, it is tempting to simply use docking techniques to generate initial bound structures for starting molecular dynamics simulations.
However, timescales for binding mode interconversion are usually slow compared to MD/free energy timescales, meaning that simulations started from different potential binding modes are likely to yield disparate computed binding free energies~\cite{mobley2006use, palma2012computation, mobley2012perspective, gill2018binding} .
And docking techniques are good at identifying sterically reasonable potential binding modes, but still perform relatively poorly at identifying a single dominant binding mode \emph{a priori}.~\cite{}

@@

	\item \href{http://getyank.org/latest/index.html}{YANK} is a tool developed by John Chodera and group on the top of OpenMM MD package. It allows the users to write their inputs in easy-to-use YAML format\cite{}.

>>>>

%%%%%%%%%%%%%%%%%%%%
%  Introduction    %
%%%%%%%%%%%%%%%%%%%%
The current Overleaf document is \url{https://www.overleaf.com/5136551543vgjqbkzpmqkp}
\section{What are alchemical free energy methods?}
\label{sec:intro}
Alchemical free energy calculations compute free energy differences associated with transfer processes, such as the binding of a small molecule to a receptor, the transfer of a small molecule from an aqueous to apolar phase~\cite{zwanzig1954hightemperature}, or the effects of protein side chain mutations on binding affinities or thermostabilities. 
 These calculations use non-physical\footnote{Here, the non-physical nature of the transformation is referred to as "alchemical", a term coined by Tembre and McCammon in Ref.~\cite{tembre1984ligandreceptor}.} intermediate states in which the chemical identity of some portion of the system (such as a small molecule ligand or protein sidechain) is changed by modifying the potential governing the interactions with the environment for the atoms being modified, inserted, or deleted.

Fig.~\ref{fig:fig_what_is_alchemy} illustrates common free energy changes that may be difficult to compute with unbiased molecular dynamics methods, but are more readily tractable with alchemical methods.
In alchemical simulations, the introduction of intermediate \textit{alchemical states} that bridge the high-probability regions of configuration space between two physical endstates of interest, permits the robust computation of free energy for large transformations.
Alchemical calculations can be used in a variety of scenarios, such as: 
\begin{itemize}
\item computing the free energy of a conformational change for a molecule with a high barrier to interconversion (Fig.~\ref{fig:fig_what_is_alchemy} \textbf{A});
\item computing partition ($\log P$) or distribution ($\log D$) coefficients between environments (Fig.~\ref{fig:fig_what_is_alchemy} \textbf{B})~\cite{rustenburg2016measuring, bosisio2016blinded} 
\item or between compartments or membranes (Fig.~\ref{fig:fig_what_is_alchemy} \textbf{C})~\cite{corey2019insights}. 
\end{itemize}

@@

Subsequent work in the 2000s led to improved implementations of alchemical methods in popular biomolecular simulation packages~\cite{shirts2003extremely,shirts2005solvation,vanderspoel2005gromacs, mermelstein2018fast, wang2015accurate, hedges2019biosimspace}. 
 This foundational work, combined with the methodological, technological, and hardware improvements of the last 5--10 years, has led to an explosion of interest and direct commercial application of these technologies~\cite{wang2015accurate, fratev2019improved, schindler2020largescale, cournia2017relative, sherborne2016collaborating, kuhn2020automated}.

@@

%%%%%%%%%%%%%%%%%%%%
% Prerequesites    %
%%%%%%%%%%%%%%%%%%%%
\section{Prerequisites and Scope}
\label{sec:pre}
What can be expected from this Best Practices guide is: a good starting point for new practitioners and a reference for experienced practitioners. 
 For this propose we provide a convenient checklist (Section~\ref{sec:checklist}) to help ensure all calculations comply with currently-understood best practices for alchemical simulation and analysis. Where the best practices are currently unsettled, we highlight areas where further research is needed to identify an unambiguous recommendation.
 It can also serve as a set of best practices to ensure simulation robustness and reproducibility which reviewers may wish to consider as they evaluate papers.

 What we assume from a novice practitioner is a moderate experience with molecular simulation concepts and use of simulation packages. 
 Furthermore, basic familiarity with the principles of molecular mechanics, molecular dynamics simulations, statistical mechanics, and the biophysics of protein-ligand association are essential. If you feel unfamiliar with some of these concepts, good starting points can be found in these references~\cite{braun2019best, grossfield2018best, klimovich2015guidelines, shirts2012best}.

@@

As some of the theoretical background can seem daunting, we do, however, provide a guide to the essential theory behind alchemical free energy calculations in Section~\ref{sec:theory}.
In the remainder of this paper, we will cover topics that are key to the preparation( Section~\ref{sec:prerequisites}), choice and use of correct protocols (Section~\ref{sec:simulation_protocol_choice}), and finally the best practices that should be used in the analysis of alchemical calculations (Section~\ref{sec:data_analysis}). 
Particular focus will be given to aspects of the molecular simulations which are unique to alchemical calculations---these include the calculation of transfer free energies (hydration free energies, partition coefficients, etc.), and binding free energies (absolute and relative).

@@

For convenience we have also compiled a list of common acronyms and common symbols used throughout this paper.
\begin{tcolorbox}[title=Acronyms, colback=blue!10!white]
    {\bf CPU} --- Central Processing Unit\\
     {\bf BAR} --- Bennett Acceptance Ratio\\
     {\bf FEP} --- Free Energy Perturbation\\
     {\bf GPCR} --- G-Protein Coupled Receptor\\
     {\bf GPU} --- Graphics Processing Unit\\
     {\bf MBAR} --- Multistate Bennett Acceptance Ratio\\
     {\bf MCSS} --- Maximum Common Substructure\\
     {\bf MD} --- Molecular Dynamics\\
     {\bf RMSE} --- Root Mean Square Error\\
     {\bf MUE} --- Mean unsigned error\\
     {\bf SAR} --- Structure-Activity Relationships\\
     {\bf TI} --- Thermodynamic Integration
\end{tcolorbox}

\begin{tcolorbox}[title=List of Symbols, colback=green!10!white]
$L$ and $R$ --- generic names for ligand and receptor\\
$K_b^{\circ}$ --- binding  constant \\
$c^{\circ}$ --- standard state concentration \\
$U$ --- potential energy\\
$u$ --- reduced potential describing a thermodynamic state \\
$\Delta G$ --- Gibbs free energy (isothermal isobaric ensemble)\\
$\Delta A$ --- Helmholtz free energy (canonical ensemble)\\
$\Delta f$ --- reduced (dimensionless) free energy \\
$\Delta \hat{f}$ --- estimate from an estimator for the reduced free energy\\
$\Gamma$ --- conformation space accessible by simulations \\
$\vec{q}$ --- vector of a single configuration, i.e. $x$, $y$, $z$ coordinates of the simulation system\\
$k_B$ --- Boltzmann constant \\
$Z$ --- partition function \\
$p$ --- pressure \\
$\mu$ --- chemical potential (grand canonical ensemble)\\
$T$ --- temperature \\
$\beta \equiv (k_B T)^{-1}$ --- inverse thermal energy \\
$\vec{\lambda}$ --- alchemical progress parameter \\
$g$ --- statistical inefficiency\\
$\mathcal{O}$ --- overlap matrix\\
$C_t$ --- discrete-time-normalized fluctuation auto-correlation function\\
$\tau _{eq}$ --- integrated auto-correlation time\\
$t_0$ --- equilibration time
\end{tcolorbox}

@@

\subsection{Simulating binding events of receptor-drug systems can be computationally expensive}
Suppose you want to compute the binding affinity, or free energy of binding, of a ligand $L$ to a receptor $R$, given by:
\begin{equation}
R+L \leftrightharpoons RL.
\end{equation}
The binding constant ($K_b^{\circ}$) is given by the law of mass action as the ratio of concentrations of product $[RL]$ and reactants $[R]$, $[L]$:
\begin{equation}
 K_b^{\circ} = c^{\circ}\frac{[RL]}{[L][R]}.
\end{equation}
The standard state concentration $c^\circ$ depends on the reference state, but it is usually set to $1\,\mathrm{mol}/\mathrm{L}$ assuming a constant pressure of $1\,\mathrm{atm}$ (see also Section~\ref{sec:standardstate-restraints}).
Thus, the Gibbs free energy of binding $\Delta G_{\mathrm{bind}}$ is given by:
\begin{equation}
    \Delta G_{\mathrm{bind},L} = -k_BT\ln K_b^{\circ},
\end{equation}
where $k_B$ is the Boltzmann constant and $T$ the temperature of the system.

\paragraph{The free energy of binding can be expressed as a ratio of partition functions}
A natural though generally very computational expensive way to estimate the equilibrium constant is by directly simulating several binding and unbinding events and computing the probability of finding the receptor-ligand system in the bound state, $P(RL)$, or the unbound state, $P(R+L)$.
Assuming the volume change upon binding to be negligible, which is often the case at $1~\mathrm{atm}$ due to the incompressibility of water, then the Gibbs free energy $\Delta G_{\mathrm{bind}, L}$ is approximately equal to the Helmholtz free energy $\Delta A_{\mathrm{bind}, L}$, and we can simulate the system in a box of volume $V$ to obtain~\cite{jong2011determining}
\begin{equation}\label{eq:binding-free-energy-from-bound-unbound-probability-ratio}
    \Delta G_{\mathrm{bind},L} \approx \Delta A_{\mathrm{bind}, L} = - k_B T  \left( \mathrm{ln} \frac{P(RL)}{P(R+L)} + \ln \left( c^\circ N_{\mathrm{Av}} V \right) \right) \, ,
\end{equation}
where $N_{\mathrm{Av}}$ is the Avogadro number, and the last term corrects for the simulated concentration being different than the standard concentration.
Let $\Gamma_{\mathrm{bound}}$ and $\Gamma_{\mathrm{unbound}}$ be the set of receptor-ligand conformations $\vec{q}$ that we consider bound and unbound respectively.
The probability of a conformation $\vec{q}$ is given by the Boltzmann probability density function
\begin{equation}
    P(\vec{q}) = \frac{\exp\left( \beta U(\vec{q}) \right)}{\int_{\Gamma} \exp\left( \beta U(\vec{q}) \right) \, d\vec{q}} \, ,
    \label{eq:conf_probability}
\end{equation}
where $\beta = (k_B T)^{-1}$ is the inverse temperature, $U(\vec{q})$ is the potential energy of conformation $\vec{q}$, and the integration is over the set of all possible conformations accessible in the simulation box volume $\Gamma$, with $\Gamma_{\mathrm{bound}},\Gamma_{\mathrm{unbound}} \subset \Gamma$.
If the simulation is long enough, we expect the fraction of conformations $\vec{q}$ found in the bound state to converge to
\begin{equation}
    P(RL) = \int_{\Gamma_{\mathrm{bound}}} P(\vec{q}) \, d\vec{q} = \frac{\int_{\Gamma_{\mathrm{bound}}} \exp\left( \beta U(\vec{q}) \right) \, d\vec{q}}{\int_{\Gamma} \exp\left( \beta U(\vec{q}) \right) \, d\vec{q}} \, .
\end{equation}
After similar considerations for $P(R+L)$, we find that the ratio of visited bound and unbound conformations, in the limit of long simulations, should converge to
\begin{equation}\label{eq:bound-unbound-probability-ratio}
    \frac{P(RL)}{P(R+L)} = \frac{\int_{\Gamma_{\mathrm{bound}}} \exp\left( -\beta U(\vec{q}) \right) \, d\vec{q}}{\int_{\Gamma_{\mathrm{unbound}}} \exp\left( -\beta U(\vec{q}) \right) \, d\vec{q}} = \frac{Z(RL)}{Z(R+L)} \, ,
\end{equation}
where we have defined the \textit{configurational integral} or \textit{configurational partition function} as $Z(\mathrm{state}) \equiv \int_{\Gamma_{\mathrm{state}}} \exp\left(-\beta U(\vec{q})\right) \, d\vec{q}$.

\paragraph{Simulating binding events is computationally expensive}
While simulating binding events has been used to estimate binding affinities~\cite{jong2011determining,pan2017quantitative} or to get insights into the binding pathways and kinetics of receptor-ligand systems~\cite{teo2016adaptive,votapka2017seekr,doerr2014onthefly,plattner2015protein,dixon2018predicting}, the computational cost of these calculations is usually dominated by the rate of dissociation, which can be on the {\textmu}s scale even for millimolar binders~\cite{pan2017quantitative} and reaches the micosecond to second scale for a typical drug~\cite{basavapathruni2012conformational,hyre2006cooperative}.
Depending on system size and simulation settings, common molecular dynamics software packages can reach a few hundreds of ns/day using currently available high-end GPUs~\cite{eastman2017openmm,kutzner2019more}, making these type of calculations uninteresting at pharmaceutical drug discovery timescales.
Other methods compute the free energy of binding by building potential of mean force profiles along a reaction coordinate~\cite{woo2005calculationa,velez-vega2013overcoming,limongelli2013funnel,heinzelmann2017attachpullrelease}, but these methods require prior knowledge of a high-probability binding pathway, which is not easily available, especially in the prospective scenarios typical of the drug development process.

@@

In many cases, the quantity of interest is the change in binding affinity between a compound $A$ and a related compound $B$ (e.g., by modifying one the drug scaffold's substituents, see (Fig.~\ref{fig:fig_what_is_alchemy} \textbf{F}), which, by using Eq.~\ref{eq:binding-free-energy-from-bound-unbound-probability-ratio} and \ref{eq:bound-unbound-probability-ratio} is given by
\begin{equation}\label{eq:delta-delta-G-physical}
\begin{split}
    \Delta \Delta G_{\mathrm{bind}, AB} &= \Delta G_{\mathrm{bind}, B} - \Delta G_{\mathrm{bind}, A} \\
    &\approx -k_BT \left( \ln \frac{Z(RB)}{Z(R+B)} - \ln \frac{Z(RA)}{Z(R+A)} \right) \, .
\end{split}
\end{equation}
Note that the terms involving the standard concentration cancel out when we assume that the volume is identical for $A$ and $B$.
Predictions of $\Delta \Delta G_{\mathrm{bind}, AB}$ with non-alchemical methods generally require long simulations of both ligands, possibly through different binding pathways.
Alchemical relative free energy calculations avoid the need to simulate binding and unbinding events by making use of the fact that the free energy is a state function and exploiting the thermodynamic cycle illustrated in Fig.~\ref{fig:fig_binding_thermodynamic_cycle}.
This is apparent after rewriting Eq.~\ref{eq:delta-delta-G-physical} as
\begin{equation}\label{eq:delta-delta-G-alchemical}
\begin{split}
    \Delta \Delta G_{\mathrm{bind}, AB} &\approx -k_BT \left( \ln \frac{Z(RB)}{Z(RA)} - \ln \frac{Z(R+B)}{Z(R+A)} \right) \\
    &= -k_BT \left( \ln \frac{Z(RB)}{Z(RA)} - \ln \frac{Z(B)}{Z(A)} \right) \\
    &= \Delta G_{\mathrm{bound}} - \Delta G_{\mathrm{unbound}} \, ,
\end{split}
\end{equation}
where $\Delta G_{\mathrm{bound/unbound}}$ is the free energy of mutating $A$ to $B$ in the bound/unbound state.
Eq.~\ref{eq:delta-delta-G-alchemical} and Fig.~\ref{fig:fig_binding_thermodynamic_cycle} tell us that the difference in free energy of binding between toluene ($A$) and benzyl alcohol ($B$) can be computed by running two independent calculations estimating the free energy cost of mutating $A$ into $B$ in the binding pocket ($\Delta G_{\mathrm{bound}}$) and in solvent ($\Delta G_{\mathrm{unbound}}$), saving us the need to simulate the physical binding process of the two compounds.
In particular, the second line of Eq.~\ref{eq:delta-delta-G-alchemical} is a consequence of $\Delta G_{\mathrm{unbound}}$ being independent of the presence of the receptor in the simulation box as the definition of the unbound state assumes receptor and ligand to be at a sufficient distance for them to have no energetic interactions.
Note that, when $A$ and $B$ have different number of atoms, Eq.~\ref{eq:delta-delta-G-alchemical} implies the presence of a factor having units of volume entering both logarithms, which require unitless arguments.
However, the value of this factor is inconsequential as it cancels out in practice.

@@

Sometimes free energy calculations can provide answers that are not
readily available from experiments.  For example, type II kinase
inhibitors selectively bind to different kinases in the so-called
DFG-out conformations~\cite{schindler2000structural}.  The selectivity of such
inhibitors may be attributed either to their differential binding to
different kinases in the DFG-out conformations, or to different
stability of the DFG-out conformations of different kinases.  Let
$K_C$ be the equilibrium constant between DFG-in and DFG-out
conformations of one kinase, and $K_D^\ast$ be the dissociation
constant of a type II inhibitor against this kinase, the apparent
binding constant of this inhibitor against this kinase is then
\begin{equation}
  K_D = K_D^\ast \frac{1 + K_C}{K_C}
  \label{eqn:conformational-binding}
\end{equation}

@@

If you are unsure whether your project is feasible, as mentioned above one recommended option is to conduct a short exploratory study to assess tractability for a small
number of ligands. This can be sufficient to get an initial
idea of feasibility and accuracy of the calculations for the
proposed target.

\section{How should alchemical simulations be applied to drug discovery?}
\label{sec:drugdiscovery}
Many practitioners expect alchemical methods to provide valuable guidance for drug discovery, and to exhibit accuracy superior to most alternative approaches for suitable targets~\cite{kuhn2017prospective}. Successful application in industry may require considerable knowledge of the ``domain of applicabilit'' of free energy calculations -- where they work well and where they will not~\cite{sherborne2016collaborating}. Successful application also requires robust protocols for preparing, submitting and analysing alchemical calculations. In this regard, the issues mentioned in the previous section such as understanding the suitability and timescales to capture the structure activity relationships (SAR), and performing up-front tests of performance are all relevant to drug discovery applications. Without venturing too far into details of system setup, which is beyond the scope of this article, we highlight some critical factors affecting accuracy and successful application.

\subsection{Capturing experimental conditions}
The calculations aim to capture the alchemical change from one ligand to another as accurately as possible. Therefore, it is necessary to consider details of the experimental setup, such as pH. Biological assays are usually run at neutral pH but this is not always the case, and protein and ligand preparation protocols should reflect experimental pH.

@@

In some cases, it is tempting to simply use docking techniques to generate initial bound structures for starting molecular dynamics simulations.
However, timescales for binding mode interconversion are usually slow compared to MD/free energy timescales, meaning that simulations started from different potential binding modes are likely to yield disparate computed binding free energies~\cite{mobley2006use, palma2012computation, mobley2012perspective, gill2018binding} .
And docking techniques are good at identifying sterically reasonable potential binding modes, but still perform relatively poorly at identifying a single dominant binding mode \emph{a priori}.

@@

	\item \href{http://getyank.org/latest/index.html}{YANK} is a tool developed by John Chodera and group on the top of OpenMM MD package. It allows the users to write their inputs in easy-to-use YAML format.
